A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-11-27 pilot-publication/manuscript.Rmd
Update manuscript.Rmd
Work on table of patient sample characteristics

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
title: A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes  
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    bookdown::word_document2:
      toc: false
      number_sections: false
      reference_docx: "reference.docx"
    md_document: default
---

@@

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table X. Overall, the
number of females were X (X%), the median age was X (IQR X), and the
median ISS was X (IQR X). A total of X (X%) patients had the primary
outcome of mortality at 30 days after arrival to the emergency
department.

@@

Previous studies on the effect of in-hospital trauma life support
training on patient outcomes are observational or quasi-experimental
without a control group, with heterogeneous results
[@Ariyanayagam1992; @CioèPeña2016; @Petroze2014; VanHeng2008;
@Wang2010]. Studies from Trinidad and Tobago, El Salvador, Rwanda, and
Cambodia found no significant effect on patient mortality after
implementing in-hospital trauma life support training
[@Ariyanayagam1992; @Cioèpeña2016; @Petroze2014; @Vanheng2008],
whereas one study from China that included 820 patients found a
significant reduction in mortality, from 20 to 15%, after implementing
ATLS [@Wang2010].

>>>>

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
title: A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes  
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    bookdown::pdf_document2:
      toc: false
      number_sections: false
##    md_document: default
##    bookdown::word_document2:
##      toc: false
##      number_sections: false
##      reference_docx: "reference.docx"
---

@@

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table 
\@ref(tab:sample-characteristics). Overall, the
number of females were X (X%), the median age was X (IQR X), and the
median ISS was X (IQR X). A total of X (X%) patients had the primary
outcome of mortality at 30 days after arrival to the emergency
department.

```{r sample-characteristics, echo = FALSE, results = "asis"}
create_descriptive_table(table.data,
                         strata = "patinfo/pt_gender",
                         caption = "Patient sample characteristics")
```

@@

Previous studies on the effect of in-hospital trauma life support
training on patient outcomes are observational or quasi-experimental
without a control group, with heterogeneous results
[@Ariyanayagam1992; @CioèPeña2016; @Petroze2014; @VanHeng2008;
@Wang2010]. Studies from Trinidad and Tobago, El Salvador, Rwanda, and
Cambodia found no significant effect on patient mortality after
implementing in-hospital trauma life support training
[@Ariyanayagam1992; @CioèPeña2016; @Petroze2014; @VanHeng2008],
whereas one study from China that included 820 patients found a
significant reduction in mortality, from 20 to 15%, after implementing
ATLS [@Wang2010].
